---
title: "Developing Data Products - Course Project"
author: mdpesheva
output: ioslides_presentation
date: "2025-06-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This presentation is the Course Project of the Developing Data Products Coursera course.

It is an R Presentation generated with RStudio.

The Shiny application is available at https://mdpesheva.shinyapps.io/myapp_height/

The Shiny app source code is available at https://github.com/mdpesheva/Developing_Data_Products_Course_Project

## Overview
The application is written in Shiny, a web application framework for R.
The source code consists of two files: 

- server.R: includes the backend of a Shiny web application
- ui.R: includes the the user-interface elements

The application is hosted on shinyapps.io.
The application goal is to provide an interface to calculate the expected adult height of a child

## How the App works?
Enter family information:

- enter height of father in cm
- enter height of mother in cm
- enter sex of child of interest

Output:

- the expected height of the child as an adult following a standardized formula

## Example:

```{r simple_code, echo = TRUE}
sex='male'; height_f=180; height_m=165
if(sex=="male"){
    height_c <- (height_m + height_f)/2 + 6.5
} else {
    height_c <- (height_m + height_f)/2 - 6.5
}
height_c        
```        